\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{\vspace{-1mm}Chinmay Pawar} % Your name
\address{+1(312) 937-5354 \\ Chicago, IL (Open to relocation)} 

\address{\href{mailto:pawarchinmay27.work@gmail.com}{pawarchinmay27.work@gmail.com} \\  \href{https://www.linkedin.com/in/pawarchinmay27/}{linkedin.com/pawarchinmay27} \\ \href{https://github.com/pawarchinmay27}{github.com/pawarchinmay27}}  %
\vspace{-2mm}
\begin{document}

\vspace{-4mm}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}
\vspace{-1mm}
\textbf{Senior Software Engineer} \hfill \textbf{Jan 2022 – Aug 2022}\\
Morgan Stanley \hfill
\vspace{-3mm}
 \begin{itemize}
    \itemsep -8pt {} 
     \item Served as a Senior Software Engineer on the Vista trade engine project, designing high-performance, distributed cross-asset allocation applications for processing \textbf{20M+} daily messages.
     \item Created a scalable, multi-threaded trade engine with microservices, handling \textbf{2M+} real-time events from various external apps for live trade visualization.
     \item Improved performance by refactoring legacy code, resulting in a \textbf{90\%} reduction in execution time for a critical algorithm handling one of MS's largest client orders ever.
     \item Mentored three junior engineers for seamless team integration, conducted thorough code reviews to maintain high-quality standards.
 \end{itemize}
\vspace{-2mm}
\textbf{SDE II} \hfill \textbf{Jan 2020 – Jan 2022}\\
HERE Technologies \hfill 
\vspace{-3mm}
 \begin{itemize}
    \itemsep -8pt {} 
    \item Incorporated self-healing capabilities in the application by automatically replaying failed data extraction jobs, resulting in a \textbf{90\%} reduction in product delivery time and ensuring data integrity.
    \item Rearchitected the application design to address distributed locking and consensus challenges, enabling seamless deployment on Kubernetes pods and boosting performance by \textbf{40\%}.
    \item Established CI/CD from the ground up for the 
     application on GitLab, improving lead time by \textbf{90\%}.
     \item Redesigned and optimized existing code, leading to an exceptional\textbf{ 97\%} reduction in response time for the search feature's performance.
 \end{itemize}
\vspace{-2mm}
 \textbf{Software Engineer} \hfill \textbf{Jul 2018 –  Jan 2020}\\
Zycus \hfill 
\vspace{-3mm}
 \begin{itemize}
    \itemsep -8pt {} 
\item Built 5 asynchronous microservices using message queues for the Integration Platform product, facilitating seamless data integration from client’s ERP to Zycus’s product ecosystem.
\item Developed a distributed rate limiter, precisely curbing concurrent user requests per unit of time based on their subscribed API plans, culminating in the creation of a remarkable \textbf{2 million \$} revenue stream for the organization.
\item Implemented service discovery feature which enabled dynamically routing client’s API requests to healthy internal application servers, ensuring a \textbf{97.99} uptime SLA.
 \end{itemize}
\end{rSection} 

\vspace{-2mm}
%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------------------

\begin{rSection}{TECHNICAL SKILLS}
\vspace{-1mm}
\begin{tabular}{ @{} l @{\hspace{2ex}} l }
Programming Languages: & Java, Scala, Python, JavaScript, SQL\\
Database: & MS SQL, Oracle, Redis, Mongo DB \\
Frameworks: & Spring Boot, Hibernate, Play, Spring Security, Junit, Mockito, GraphQL\\
Tools: & Git, ActiveMQ, Docker, Kubernetes, Maven, Jira\\
Cloud Platforms: & AWS, Azure\\
Architecture: & REST, Microservices, Distributed Systems

\end{tabular}
\end{rSection}


\vspace{-2mm}
%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{RELEVANT PROJECTS}
\vspace{-1mm}
\textbf{GoLang Based Monitoring Agent: }
\vspace{-3mm}
 \begin{itemize}
    \itemsep -8pt {} 
    \item Engineered a cross-platform Golang library for retrieving system stats across servers, offering hassle-free deployment as an executable binary, eliminating server-side prerequisites.
 \end{itemize}
 
\vspace{-2mm}
\textbf{GraphQL Query Tool:}
\vspace{-3mm}
 \begin{itemize}
    \itemsep -8pt {}
    \item Designed a GraphQL dashboard for engineering teams to access production environment's information, resulting in a remarkable \textbf{95\%} reduction in application deployment time and enhanced operational efficiency.
 \end{itemize}
 

 \end{rSection} 

\vspace{-2mm}

% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Master of Information Systems}, University of Illinois Chicago \hfill {Dec 2023}  \newline 
{\bf Bachelor of Computer Science and Engineering}, Mumbai University \hfill {Jul 2018} 
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

\vspace{-2mm}




\end{document}
